### 2017-10-18 Draft2/Appending.Dynamic.tex
Proof-ize some things

[lemma]
Let $\listname$ by a dynamic array. As $\varnitems$ are appended, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.

[proof]
The capacity starts out at zero and becomes $\initcapacity$ once one element is appended. From then on, it can only grow by a factor of $\growthfactor$ via $\FuncGrow$, so if $\growthfactor^i\initcapacity$ is the current capacity then $\growthfactor^{i + 1}\initcapacity$ must be the next capacity. By induction, the rest of the sequence is $$\left\{ \growthfactor^i\initcapacity \right\}_{i = 1}^k$$ for some $k$. Since the capacity is only as big as is needs to be, namely greater than or equal to $\varnitems$, $k$ is the smallest integer for which $\growthfactor^k\initcapacity \geq \varnitems$. Using this property, I now derive $k$.

@@

Then the final term in the sequence is $\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$, completing the proof.

@@

From [lemma] I know the exact capacities $\listname$ takes on as $\varnitems$ items are appended. Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated. Then the total length of arrays allocated is

>>>>

\begin{lemma}
\label{CapacitySequence}
	Let $\listname$ by a dynamic array. As $\varnitems$ items are appended, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.
\end{lemma}

\begin{proof}
	The capacity starts out at zero and becomes $\initcapacity$ once one element is appended. From then on, it can only grow by a factor of $\growthfactor$ via $\FuncGrow$, so if $\growthfactor^i\initcapacity$ is the current capacity then $\growthfactor^{i + 1}\initcapacity$ must be the next capacity. By induction, the rest of the sequence is $$\left\{ \growthfactor^i\initcapacity \right\}_{i = 1}^k$$ for some $k$. Since the capacity is only as big as is needs to be, namely greater than or equal to $\varnitems$, $k$ is the smallest integer for which $\growthfactor^k\initcapacity \geq \varnitems$. Using this property, I now derive $k$.

@@

	Then the final term in the sequence is $\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$, completing the proof.
\end{proof}

@@

From \ref{CapacitySequence} I know the exact capacities $\listname$ takes on as $\varnitems$ items are appended. Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated. Then the total length of arrays allocated is

### 2017-10-18 Draft2/Appending.Growth.tex
Proof-ize some things

[That lemma] still holds, since all of the assumptions made there are also true for growth arrays. In particular, although growth arrays grow differently than dynamic arrays, the following claim is still true:

[other lemma]
The capacity of a growth array grows by a constant factor $\growthfactornew$ after the first time it is called.

[proof]
I prove that the algorithm ensures this using induction.

@@

For $i \geq 2$, given the algorithm behaves correctly the $i$th time it is called, I wish to show it behaves correctly the $(i + 1)$th time. From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\growthfactornew^i\initcapacitynew$ and the head capacity is $(\growthfactornew^i - \growthfactornew^{i - 1})\initcapacitynew$. The next (total) capacity should be $\growthfactornew^{i + 1}\initcapacitynew$, and the next head capacity should be $(\growthfactornew^{i + 1} - \growthfactornew^i)\initcapacitynew$, which is $\growthfactornew$ times the current head capacity. The algorithm determines the capacity of the next buffer in this manner, proving the inductive step and completing the induction.

>>>>

\ref{CapacitySequence} still holds, since all of the assumptions made there are also true for growth arrays. In particular, although growth arrays grow differently than dynamic arrays, the following claim is still true:

\begin{lemma}
	The capacity of a growth array grows by a constant factor $\growthfactornew$ after the first time it is called.
\end{lemma}

\begin{proof}
	I prove that the algorithm ensures this using induction.

@@

	For $i \geq 2$, given the algorithm behaves correctly the $i$th time it is called, I wish to show it behaves correctly the $(i + 1)$th time. From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\growthfactornew^i\initcapacitynew$ and the head capacity is $(\growthfactornew^i - \growthfactornew^{i - 1})\initcapacitynew$. The next (total) capacity should be $\growthfactornew^{i + 1}\initcapacitynew$, and the next head capacity should be $(\growthfactornew^{i + 1} - \growthfactornew^i)\initcapacitynew$, which is $\growthfactornew$ times the current head capacity. The algorithm determines the capacity of the next buffer in this manner, proving the inductive step and completing the induction.
\end{proof}
